ZCB Pricing

### 2018-07-25 ZCB Pricing .Rmd
Updated CN and some Comparisons with MCs

  # C_1 <- matrix(0,nrow = M,ncol = 1)
  # C_1[1,1] <- -pd(1)
  # C_1[M,1] <- -pu(M)
  # 
  # C_2 <- matrix(0,nrow = M,ncol = 1)
  # C_2[1,1] <- pd(1)
  # C_2[M,1] <- pu(M)

  for (i in 1:(length(I)+1)){
    Inv <- solve(Diag_1)
    RHS <- Diag_2%*%Bond_values 
    Bond_values <- Inv%*%RHS
  }

@@

compare_mat <- matrix(NA,nrow = 10, ncol = 8) # matrix of comparison

colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations")

a = 0.01
b = 0.1
s = 0.04
t= 0
T = 1

for (j in 1:10){
  compare_mat[j,1] <- a
  compare_mat[j,2] <- b
  compare_mat[j,3] <- s
  compare_mat[j,4] <- 0.01 +0.01*(j-1)
  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
  start_time <- proc.time()[1]
  compare_mat[j,6] <- monte_carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4], n = 1000, s=250)
  compare_mat[j,7] <- proc.time()[1] -start_time
  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
}

>>>>

  # C_1 <- matrix(0,nrow = M,ncol = 1)
  # C_1[1,1] <- -2*pd(1)
  # C_1[M,1] <- -2*pu(M)
  # 
  # C_2 <- matrix(0,nrow = M,ncol = 1)
  # C_2[1,1] <- pd(1)
  # C_2[M,1] <- pu(M)
  Inv <- solve(Diag_1)

  for (i in 1:(length(I))){

    RHS <- Diag_2%*%Bond_values 
    Bond_values <- Inv%*%RHS
  }

@@

compare_mat <- matrix(NA,nrow = 10, ncol = 10) # matrix of comparison

colnames(compare_mat) <- c("Alpha","Beta","Sigma","Initial rate","Known Price","Monte Carlo"," MC System Time","MC Squared Deviations", "Moment Matching", "System Time")

for (j in 1:10){
  compare_mat[j,1] <- 0.08
  compare_mat[j,2] <- 0.8
  compare_mat[j,3] <- 0.005
  compare_mat[j,4] <- 0.01 +0.01*(j-1)
  compare_mat[j,5] <- bond_price(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], t= 0, T = 1, r = compare_mat[j,4])
  start_time <- proc.time()[1]
  compare_mat[j,6] <- Crude_Monte_Carlo(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
  compare_mat[j,7] <- proc.time()[1] -start_time
  compare_mat[j,8] <- (compare_mat[j,6] -compare_mat[j,5])^2
  start_time <- proc.time()[1]
  compare_mat[j,9] <- Moment_Matching(alpha = compare_mat[j,1],beta = compare_mat[j,2], sigma = compare_mat[j,3], T = 1, r0 = compare_mat[j,4], n = 1000, s=250)
  compare_mat[j,10] <- proc.time()[1] - start_time
